Conformal Counterfactual Explanations

### 2023-03-22 paper/paper.tex
sorted out citations. Had to convert bibliograhy to bibtex
progress on paper

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath}

@@

Solutions to Equation~\ref{eq:general} are considered valid as soon as the predicted label matches the target label. A stripped-down counterfactual explanation is therefore little different from an adversarial example. In, for example, generic counterfactual search as in \citet{wachter2017counterfactual} has been applied to MNIST data.

@@

@@

\bibliographystyle{plainnat}
\bibliography{../bib}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath}
\usepackage{graphicx}

% Bibliography
\bibliographystyle{plainnat}
\setcitestyle{numbers,square,comma}

@@

Solutions to Equation~\ref{eq:general} are considered valid as soon as the predicted label matches the target label. A stripped-down counterfactual explanation is therefore little different from an adversarial example. In Figure~\ref{fig:adv}, for example, generic counterfactual search as in \citet{wachter2017counterfactual} has been applied to MNIST data.

@@

\begin{figure}
  \centering
  \begin{minipage}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{www/you_may_not_like_it.png}
    \caption{You may not like it, but this is what stripped-down counterfactuals look like. Counterfactuals for turning an 8 (eight) into a 3 (three) using different methodologies. Left: Using the generic approach proposed in \citet{wachter2017counterfactual}. Center: Using REVISE \citep{joshi2019realistic} with a well-specified surrogate. Right: Using REVISE \citep{joshi2019realistic} with a poorly specified surrogate.}\label{fig:adv}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{www/mnist_9to4_latent.png}
    \caption{Using surrogates introduces a dependency. Counterfactuals for turning a 9 (nine) into a 4 (four) using REVISE: original image (left); counterfactual using a well-specified surrogate (center); and counterfactual using a poorly specified surrogate (right).}\label{fig:vae}
  \end{minipage}
\end{figure}

\bibliography{../bib}

@@
